\documentclass{article}
\usepackage{amsmath}
\usepackage[ampersand]{easylist}
\ListProperties(Hide=100, Hang=true, Progressive=3ex, Style*=$\bullet$ )
\usepackage{amssymb}
\title{AIProject v2.0 Development}
\date{11/18/2014}
\begin{document}
\maketitle

\section*{Tests}
\begin{easylist}
& RandomWalk $\square$
& MountainCar $\square$
& Poker $\square$
& Pole Balancing $\square$
\end{easylist}

\section*{Todo}
\begin{easylist}
  & \texttt{11/19/2014} Ammending the Environment Module.
  && Modify the Sensor modules. There are some problems such as unused methods in base class for right reasons.
  && Make SensorBase more agnostic, e.g. shed isState function, since this is of no use when the domain of the state is undetermined.
  \\
  && ActuatorBase should also be ammended to capture the problem.
  && As to the tests. Fuck them all. Rewrite the tests so it can be used as an example to the API users.
  \\ 
  && Change template for both actuator and Sensor to $<S, A>$.
  \\
  && Actuators don't need to be overrided for most cased due to Environment, so delete all of them if needed.
  &&& ActuatorRandomWalk
  \\
  & \texttt{11/22/2014} 
  && I'm on the $2^{nd}$ chapter of Linear Programming book. I have an inefficient idea on how to find all extreme points (basically, its a disgusting ${n \choose m}$, $n$ is the number of columns and $m$ is the number of rows). I'm sure the second chapter will have a better approach to this.
  && I'm also currently working on my own graphics library for a lot of reason. (opengl game, windowing system, testbed). This will also serve as a testbed for the tests here.
\end{easylist}

\section*{Pre-Requesite}
\begin{easylist}
  & boost-1-55
  & 
\end{easylist}

\section*{Log}
\begin{easylist}
& 11/18/2014
&& Prefected (for now) Graph modules.
&& Removed DP from design. It seems that DP is not very general as opposed to LP.
&& Create Environment class.
&&& After doing so, introduce formal game test.
& 11/22/2014
&& Optimization is implemented. SarsaETGD\_test from 2.5-3s to 1.7s.
&& A faster way is possible by taking advantage of buildActionValues and produce max value as well.
&& Another optimization. 1.7s to 1.19s. HUGE improvements.
&& By modifying loops and some simple loop unrolling, I've managed to optimize further from 1.19s to 0.97s. I will stop optimization for now. I don't see any more imporovements. And very unlikely that I'll find one in the future.
\end{easylist}

\section{Vocabulary:}
\begin{easylist}
  & Generalization: In tile coding, samples are taken around grid points. By default, the radius of influence is 1.0. If more thatn 1.0, radius of influence is bigger.
  & Control Policy: Policy for selecting action online.
  & Learning Policy: Policy for selection action offline.
  & 
\end{easylist}

\end{document}
